biological data preperation

### 2019-01-14 src/biological_data_prep.Rmd
re-ran loop. confirmed some dont have data

    }
}
data_aea <- as.data.frame(data_aea_sp)
write.csv(data_aea,"../output/bio/presence_points_without_envdata_relooped.csv", row.names = FALSE)
head(data_aea_sp$chl_depth)
```
note that if you wanted to just loop through the netcdfs and create a ton of raster bricks with the same name as the netcdf, the following code you wrote before works

netcdf_list <- list.files("../data/env/netcdf", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/env/netcdf", pattern = '*.nc', full.names = FALSE) #false means the path is not included
library (ncdf4)
for (i in 1:no_netcdf) {
  print(netcdf_name[i]) #this just prings the name of the netCDF R is working on
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  temp_brick <- projectRaster(temp_brick, aea) #aea is an existing raster in the projection I want that I created (environmental_data_preperation)
  assign(netcdf_name[i], temp_brick) #this asigns the netCDF name to the raster brick
}

```{r}

change dataset back into a dataframe and then save as a .csv

```{r}

>>>>

    }
}
data_aea <- as.data.frame(data_aea_sp)
write.csv(data_aea,"../output/bio/presence_points_without_envdata_relooped.csv", row.names = FALSE)
head(data_aea_sp$chl_depth)
```

see if it has made a difference

```{r}
presence_wdepthv3 = data_aea[!is.na(data_aea$depth), ]
nrow(presence_wdepthv3) #10178 rows - same as before whcih is good
head(presence_wdepthv3)
```

```{r}
presence_wdepth_nochl3 <- presence_wdepthv3[is.na(presence_wdepthv3$chl_depth), ]
nrow(presence_wdepth_nochl3) #just to check it has mapped
presence_wdepth_noo23 <- presence_wdepthv3[is.na(presence_wdepthv3$o2_depth), ]
nrow(presence_wdepth_noo23) #just to check it has mapped
presence_wdepth_nosalinity3 <- presence_wdepthv3[is.na(presence_wdepthv3$salinity_depth), ]
nrow(presence_wdepth_nosalinity3) #just to check it has mapped
presence_wdepth_notemp3 <- presence_wdepthv3[is.na(presence_wdepthv3$temp_depth), ]
nrow(presence_wdepth_notemp3) #just to check it has mapped
```

It used to be
[1] 2394
[1] 2394
[1] 3133
[1] 3109
so actually a minor change (maybe this is because you added the dec 2015 data in - it wasn't available before). ok need to redo checks...
